\documentclass{amsart}

\usepackage[a4paper,margin=15mm]{geometry}
\usepackage{multicol}
\usepackage{tabularx}
\usepackage{fontspec}

%% \usepackage{libertine}

\setmainfont{TeX Gyre Schola}[Scale=0.85]

\title{The Brasknova Complex}
\author{Ross Alexander\\Agent Blue\\Brightstone Shard}
\date{December 23, 2005}

\begin{document}

\maketitle

\begin{multicols}{3}

\setcounter{collectmore}{10}
  
\section{Immediate Instructions}

At 19:10 GMT a B-4 Ghost, having flown the secret American base in the
Tora Bora mountains, in Mujahadeen controlled Afganistan, has been
lost over Siberia.  The experimental plane was testing Soviet long
range radar and had a crew of three.  The plane was not armed with
nuclear weapons but did have a full complement of standard bombs and
missiles, including two 15,000 lb bunker busters, five cluster bombs,
two dozen 1000lb JDAMs, two Storm Shadow HARM missiles and four
Sidewinders.  A secret backup system in the plane reported all systems
were working as of 20:00 GMT.

The National Security Council has authorized the immediate
reactivation of the PD236 Shard known as Brightstone.  Their
objectives are the following.

\begin{enumerate}

\item To enter the Soviet Union using any possible means.  Extremely
limited time constaints limit the entry point to East Berlin.

\item To collect equipment originally slated for NME (Nuclear Materials
Extraction) operation in Iraq.

\item Travel to Brasknova Military Complex, situated in the western
Urals.

\item Determine the reason for forced landing, including the
possibility of espionage.  Eliminate any traitors and rescue any
captives.

\item Travel to Brasknova Long Range Bomber Airbase.  Destroy
any possible installations which could impeed escape.

\item Fly B-4 back to designated safe airfield.  Destroy plane if this
cannot be done.

\end{enumerate}

\subsection{Local Conditions}
With a possible invasion by the Red Army and large build up of NATO
forces in both England and continental Europe all Shard operators have
been put on immediate standby.  A full state of emergency may be
imposed at any time, with a possible state of war and full
mobilisation in Germany.

The weather across Europe is bitterly cold with storms and heavy snow
expected and a white Christmas is London almost a certainty.  The
current temperature in Berlin is -10\textdegree{} celcius, dropping to
-30\textdegree{} celcius in Moscow, with overnight temperatures
further east falling to -45\textdegree.  Daytime temperatures in
Siberia are not expected to rise above -20\textdegree.

Currently there all access routes in and out of Berlin are open but
poor weather is making air travel difficult.  The airbase at Gatow in
the British Sector (actually part of the expanded American Sector but
its still called the British Sector to meet the requirements of
Potsdam) is still processing military flights, however fighter escorts
are not available.  The risk of engagement is currently set at low,
but not zero.

\section{Background Information}

With the imminent formation of the United States of Europe on 1st of
January timing could not be worst.  The vast Soviet-China
Confederation has been massing forces near its border for some time
and military analysts know that western forces are completely out
numbered.

The 1989 uprising in communist Eastern Europe had been crushed after a
young KGB agent organised an overthrow of Gorbachov.  Since then the
Soviet Union under chairman Putin has completely rebuild the army
after its withdrawal from Afganistan.

In response to the hardening of the Iron Curtain the western European
counties have been rapidly converging, with montary union in 1989 and
coming political union.  The continuing troubles in the Balkans are a
sore point for both sides but strained ties have meant that concerted
action has not been forthcoming.

When communist agents assasinated King Charles during his coranation
in 1994 the future king William abdicted.  With the monachy in crisis
the Union was closing to dissolving.  When France and Germany declared
that they would form a political union, starting with removing
internal borders and then currency union, the pound crashed.  Faced
with a currency crisis and massive political instability the United
States feared its staunchest ally would go under.  With the US economy
booming and the dollar all powerful England, Scotland, Wales, Ulster
and Ireland became the 57th, 58th, 59th, 60th, 61st and 62nd States
after the seven former Canadian provences.  In 1998 Quebec, having
tried to go it along for less than ten years, became the 63rd State.

With the CIA in disgrace after been exposed as setting up Monica
Lewenski and forcing President Clinton to resign a number of Black
Operations groups were formed under the umbrella PD 236.  Each Black
Operations cell is known as a Shard.  People working as agents for PD
236 operations are expected to continue with the normal jobs and lives
and the cell is only assembled for a specific operation.  It is very
rare for any two operatives to work together more than once.

The Brightstone Shard was originally organised to do an extraction of
plutonium from Iraq six months previous but before it could be formed
Isreal destroyed the plant, and nearby Baghdad, with a 80 megaton
ground burst nuclear weapon.  However, under PD 236 rules, its members
had to be put on stand down for two years.  All the equipment that had
been assembled for the mission, secretly shipped into Soviet Union at
the port of Odessa had to be left there.  Immediately afer the
Isrealli attack the Red Army fully mobilised, and is still currently
intercepting all vessels crossing the Black Sea.  Spies within the
city report that the container is still currently untouched except for
environmental damage caused by its position on the open docks.

As has always been the case Berlin is still the outlier and the
crucible of Cold War intrigue.  The Wall has been revamped after its
damage during the 1989 uprisings but very careful work by PD 236 cells
in West Berlin have uncovered a network of Nazi era bunkers under the
wall near where the Reich Chancellery once stood.  These deep level
bunkers are believed to have been used by Bormann to escape and
represent the best possible way to getting under the wall.

\section{The Original Brightstone Cell}

Below is a precis is the original Iraq team.  It may be necessary
to recruit other PD236 operatives as the notice on this operation
is limited to three hours.


% ----------------------------------------------------------------------

\subsection{Michael Stephenson --- Agent White}

Born in Durham Michael Stephenson joined the Army at 17 and served six
tours of duty, including three in Northern Ireland, one in Cyprus, and
two in West Germany.

% ----------------------------------------------------------------------

\subsection{Raj Patel --- Agent Green}

Born in Southhall, London and later brought up in Harlesden.  Started
working as a document courier before being recruited to join a
corporate security team.  Currently working for a major international
investment bank based in City of London and the Docklands.

% ----------------------------------------------------------------------

\subsection{Aaron Wade --- Agent Orange}

Born in Fargo, North Dakota.  Did basic training in the army before
studying in medicine at the University of Minesota at Deluth.
Seconded into the industrial-military complex to work on chemical
weapons, working at a major industrial corporate in the twin cities.
Currently serving at Porton Down with the Army.

% ----------------------------------------------------------------------

\subsection{Kozo Yashida --- Agent Cyan}

Born in Osaka from parents belonging to the Aum Shinrikyo cult.
Trained in firearms by the cult before it was disbanded with the
execution of its leader.  Freelance investigator, working for Japanese
Zibatsu to track down corporate leaks and deal with them in the most
expedient manner.

% ----------------------------------------------------------------------

\subsection{Mary Summerfield --- Agent Black}

Born in the highlands of Scotland and a fervent member of the Free
Scotland movement.  Growing up the wild west of northern Scotland she
was one of the boys and trained in the physical of the martial arts.
Officially a Federal Marshall, she actually works for MI5, but
actually reports to the NSA, keeping track on possible inflitration of
the early warning systems and anti-ballistic missile sites in northern
scotland.  Still has extensive contact and sentiment for the
underground Scotland Nationalist Movement.

% ----------------------------------------------------------------------

\subsection{Alise O'Conner --- Agent Yellow}

Born in South Armagh to a Catholic family and joined the IRA at the
age of 14.  Trained in handling explosives and maintaining the IRA's
secret weapons arsenals.  With Northern Ireland becoming the State of
Ulster the IRA lost much of its support but continued its war with the
UDA and the other paramilitary groups over various criminal
operations.  Currently based in Kilburn, London and supplies arms and
explosives for dealing with Yardie groups involved in the drugs trade.

% ----------------------------------------------------------------------

\subsection{Huang ``Kitty'' Wong -- Agent Pink}

Born in Shanghai, smuggled into Hong Kong as a child and moved to
London after the 1997 hand back of the province to China.  Studied at
UCL, completed an MD at John Hopkins and is currently working at
Imperial College in nanotechnology.

% ----------------------------------------------------------------------

\subsection{Macy Down -- Agent Purple}

Born to a leading Civil Rights Movement activist in Alabama.  Was
attacked by the resurgent Ku Klux Klan as a teenage girl. Trained in
martial arts, becoming a national champion.  Retired after suffering
injury and currently works for Amnesty International in London.

\section{Berlin}

The Shard must cross into East Berlin before taking a train into the
Soviet Union.  All flights out of East Berlin are rigorously screened
and all passengers need transit visas to travel.  This requirement is
not enforced on the railways.  Road travel is also possible but
anything smaller than a truck or a bus will not be able to travel
under the current conditions.

All trains leaves from Hauptbahnhof near Alexanderplatz, departing
across Poland to either Kiev or Minsk roughly every two hours.  An up
to date timetable is essential.

There is currently a division of Red Army Paramilitaries in Berlin as
well as the usual Stasi.  The GRU and KGB are also in force in Berlin
but do not work well together.

There are a number of possible ways of entering East Berlin, from
taking the Intourist bus, the abandoned U-bahn tunnels to the secret
passages though the Hilter Bunker.  An earlier PD236 cell surveyed the
area around Potsdam Platz while installing cabling for Deutche
Telecom.  This did not not cover the area under the wall and
no-mans-land but it did find the western exit to one of the passages.
An extrance to the tunnel was installed in the Tiergarden but it has
not been check for many months.

Every member will be provided with three sets of identity cards and
passes.  The first is fake western ID cards (passports for British,
drivers licenses for continental Americans).  The next is an East
German ID card.  This does not allow people to travel within the
security zone but ever one does have an occupation which will give
them reason to be out outside normal hours.  The last are Russian
military passes.  The passes are for a detactment currently involved
in guarding the Chinese border.  This is currently a low risk but very
dull, poorly provisioned and poorly paid assignment.

Internal Soviet Union flights require transit visas but the checking
is not automated or centralised, and internal air travel security is
poor.  Military activity always takes precidence over civilian traffic
so delays are common place and to be expected.

\section{Odessa}

Odessa is the home of the Black Sea fleet, most of which are currently
on patrol.  It is also a major port, taking cargo from all the
countries on the Black Sea, including Turkey, a NATO member.  With the
onset of winter and the current military situation the level of
traffic is severely reduced but oil tankers from Iran, Libya Romania
are still vital.  Cargo ships, including sugar from Cuba also continue
to dock, but the number of container carriers is down to a trickle.
This is both good and bad.  The container docks are now virtually
unpopulated, with most of the staff currently laid off.  This will
make it very obvious that that stangers are are on the docks, as
all those working there know each other very well.  The lack of
internation trade has cut the amount of foreign goods and currency
entering the port, and with smugglers keeping a very low profile
few bribes are forthcoming.  Morale at the docks is extremely low
and corruption is rife.  Remember that the KGB are not too
likely to be around but the GRU are probably there in force.

\section{The Brasknova Complex}

The Brasknova Complex is build in the western side of the Ural
mountains.  It is a vast industrial-military complex which includes
chemical and nuclear weapons manufacture, long range radar and
interceptor missiles.  A long range bomber installation is about 15
miles away.  The complex also contains numerous nuclear bunkers and a
backup command and control center.

\subsection{Nuclear Reactor Plant}

This plant is getting on in years, and is now over forty years old.
It is in a poor state of repair and is known to leak radiation on a
regular basis.  It is one of the original fast breeder reactors which
the Soviet military used to create weapons grade plutonium.  However
the amount of space required to store its spent fuel rods means that
it cannot house any excess material.  Since the START III agreement on
arms limitations there has been a surplus of weapons grade nuclear
material.  There are rumours that there storage facilities accessable
near the complex which contain both high grade waste and usable
material.  The plant currently generates electricity for the complex
and nearby area.  The plant is connected to the Soviet power grid but
the age and repair of the switch gear limit the ammount of power which
can be flow between Brasknova and the grid.

The plant is quite small, generating about 400MW, and has only one
reactor and associated cooling system.  After the Chenobyl disaster
the plant was given an overhaul but has not had any major repairs
since then.  The reactor container is now highly radioactive and
anybody entering the main reactor building without a full radiation
suit will be exposed to a lethal dose.  An large underground storage
facility to the north of the reactor contains fresh water.  As the
water is mostly snow melt is mostly polution free and this has the
turbines and other hydrostatic systems to keep running without too
much cleaning.  The water also supplies the complex and associated
bunkers.

There are about a dozen permanant workers at the plant, who work in
shifts.  The plant is not well guarded and the electronic monitoring
of the area has mostly malfunctioned due to raditation exposure.

\subsection{Chemical Works}

The Chemical Works Complex (CWC) is a substantial complex of buildings
and pipes.  It was originally used to create chemical weapons, mainly
sarin derivate nerve agents.  With the signing of the Chemical Weapons
Ban Treaty it no longer manufactures any chemical weapons, but it does
have considerable stock piles of various lethal and non lethal
chemical weapons.  A few are in shells but most now sit in rusting
drums, many left out in the open.

The plant now manufactures drugs, mostly amphetemines, such as speed
and estacy.  The plant was converted using North Korean, originally
Japanese, technology in 1995 and is mostly automated.  There are still
a large number of staff, numbering over 100, running the plant but
about half the plant is currently shutdown.  The plant contains a
packing and warehouse area and semi regular shipments are made from
the area.  Most of the staff are prisoners as most of the work is
menial.  The security around the plant as a whole is fairly poor but
the actual working areas have modern (for Soviet) electronic security.
As theft from the plant is docked for the security personel pay the
guards are brutally dilligent, but even so corruption is rife and many
tabs go onto the black market though doctored documents.

It is rumoured at housed in one of the closed buildings is a secret
chemical and biology weapons labortory.  The facility is connected to
a number of bunkers and the rumour states that one of these bunkers
contains some of the top Soviet scientists.  Diligent monitoring of
incoming and outgoing material suggests that there is a lot of
unaccounted for goods movements but corruption and incompentence are
so rife is it almost impossible to determine was is official secret
traffic and what is just smuggling.

\subsection{The Airstrip}

With a large airbase nearby the airstrip is not heavily used.  It is
not very long and is only tarmac, not concrete, so only small planes
(up to 20 people) can fly from it.  It is reasonably easy to take off
from the airstrip provided the plane climbs immediately but it is
quite tricky to land as the complex is surrounded by close mountains.
A pilot must come in slow over the mountain top and cut the power
almost immediately after clearing the peaks.  As there are always
cross winds over the mountain tops this can lead planes to drift off
course and comes down into the side of the bowl.

The airstip has one hanger with two permanant mechanics.  Normally
there are two four seater planes and one ten seater jet stationed at
the airstrip, mainly used to ferry VIPs, but it can have as many as
seven aircraft.  There is always one four seater prop plane at the
airstrip as it is used for doing avalanch surveys and ferrying goods
from the airbase when the road is closed.  Because of the enclosed
nature of the area there is no radar or air traffic control.  There is
a radar station and surface-to-air missile site on the peak to the
north of the complex but this is controlled by the airbase.

Because of the importance of the planes the hanger is well guarded.  A
permanant detachment of paratroopers are housed in barracked on the
farside (eastern edge) of the airstrip in their own self contained
barracks.  They have their own small hanger with two light planes.
These troops consider themselves the top boys of the area and do not
work with the other troops in the area.

\section{General barracks}

At the southern end of the complex area is the main barracks and staff
housing.  At the lowest level is what could be considered Brasknova
township.  There is a number of shops, including a butcher, a baker, a
general store and even a small brewery.  The brewery has a small bar
and the bakery has a small eating area.  Directly above the stops
(going up the hillside) are the main barracks.  These house all the
workers and security staff.  In addition there is a detectment of
regular troops housed there.  These are part of the mountaineering
division and trained to launch covert operations in mountainous areas.
Most are veterans of Afganistan and while are hardened fighters have
little stomach for the actual military.

Further up again are the bunker entrances and beyond them are the
staff houses.  Unlike the concrete, five story buildings they overlook
these are two story detached houses.  Most are walled and kept in good
condition.  Right at the top are a number of large houses, sitting on
plataux cut from the mountainside.  They have no direct outside
access.  These plush buildings are three story wooden detached houses
in meticulate condition.  All are over sixty years old but are by far
the best kept buildings in the area.

\subsection{Command and Control}

The main C\&C area is built into the mountain with only a small
concrete front in the open.  The entrance contains various security
checks and resembles a large hall, going into the mountainside.  At
the end of the hall is a vast steel door, atleast a metre thick.
Beyond that a 20' by 20' coridor runs another fifty metres in,
reaching another steel door.

The C\&C serves as both a backup to the air defense systems at the
airbase and the a general military control center, to be used in the
event of a nuclear strike against Moscow.  The original air defense
system dates from the late 1970s but the main C\&C was build during
they mid 1990s.  The Soviets realised many of their existing C\&C
centers were vulnrable to the American bunker buster JDAMs, especially
the MOAB.  This was amply demonstated when the Libyian chemical
weapons facility built by the Soviets in the Atlas mountains was
destroyed by a single 21,000 lb guided bomb, dropped by a B-2 stealth
bomber.

The center contained (at the time) the latest in Soviet computer
technology (appoximately 15 years behind the latest in free world).
Rather than build a single communications facility the center is
connected to over a dozen radio, microwave and satellite stations
using fibre optic cable.  The center has its own supplies, including
fuel cell generators.  Because of its secret nature the center is
not offically part of the standard military command, but is instead
controlled by the State Protection Directorate.  This group tends
to suffer from funding difficulties, with a few years of largess
to break the general state of under funding.  As such, it tends to
have very good equipment it can't afford to maintain.

With the recent heating up of the cold war the center has been
reinstated but is not known whether it it actually up and running,
given that ten years of neglect will take a long while to reverse.
The relatively modern state of the center means it is a popular place
to work, despite its bleak surroundings, as has a staff of at least
50, with up to 300 places available when fully functioning.

\subsection{Other Facilities}

Both the KGB and the GRU each have their own buildings here.  These
buildings are mostly self contained, with underground parking, prison
cells, bunker with connection to their own deep bunker, work area and
staff accomodation on the top floors.

There are three of these buildings, containing the KGB, GRU and the
Communist party respectively.  Their staff avoid each other and
everybody else avoids them.  Almost all the staff end up here because
they lost out in some dirty little official politics back stabbing.
Most are middle ranking aparachiks with enough influence to have
stopped them from simply being shot, but little more.

\subsection{The Underground Facilties}

The mountains around Brasknova are riddled with tunnels, some large
enough to drive a truck down, most others little wider than a single
person.  Originally built as a secure facility against the Nazi
invasion in the Great Patriotic War it was a major staging area should
Moscow have fallen.  They were then expanded into full nuclear
bunkers, capable of supporting a large number of people for many
years.  In the 1980s a number of additional access routes were opened
up, including a major road tunnel from the airbase plus a number of
small tunnels leading down onto the plains both east and west.

However the lack of a central facilties maintainance group as meant
that many of the bunkers and tunnels are in poor condition, with each
group maintaining only their own rooms and access routes.  This has
meant that there is no central security, with no electronic security
or access control.  Most security is lock and key, with a few having
electronic passes or micro computer controlled panels.  All the main
tunnels and rooms are built using reinforced concrete and are almost
totally impregable to force, but lighting and ventilation is at best
patchy so most rooms are empty.

\subsection{The Airbase}

Unlike the Brasknova Complex the Brasknova Airbase is under a single
command and while not the pride of the airforce, is a major asset.  As
well as major stategic bomber base its location makes it an ideal
transit point, with military flights refueling and changing crew.
While the prevailing westerly wind makes subject to crosswinds it does
keep the place clear of deep snow.

The airbase has the latest in long range radar and directly controls
the airspace over the Urals as well as being part of the early warning
system.  Connected to the early warning system are four batteries of
surface-to-air missiles, one of which is the latest anti-ballistic
missile system.  These hypersonic missiles are designed to destroy
MIRVs as they re-enter the atmosphere, before they a chance to deploy
their warheads.  No information is available, official or otherwise,
about their reliability and while official propaganda states they are
better than the American SDI interceptors the well publised
difficulties the Americans are having with their missiles suggest
these are more for show than any real effect.  Recent analysis
suggests that they may in fact be tactical nuclear weapons, following
the maxim that it takes a nuke to kill a nuke.

The long range bomber fleet is now old, being turboprops build during
the late 1970s.  Like most of Soviet engineering, they are solidly and
simply built, with every little in the way of modern avionics.  The
facility does however hold an enoumous stock of spares and well
equiped workshops so all the planes are in good working order.
Ironically, the nuclear bombs they are suppose to carry are now very
old and unrealiable, since only a very limited number of people are
allowed to work on them.

About half the fleet has been converted into conventional bombers, and
have seen active service over Afganistan doing carpet bombing raids.
Their turboprop design limits their working altitude and speed but all
carry extended range fuel tanks and have a range of over 12,000 miles.

The radar and early warning facilities are a patch work of
technologies, ranging from simple analog equipment dating back to the
late 1940s to digital super computer designed to calculate incoming
trajectories.  The associated communications facilties are the same,
with a few fibre cables, many distance analog lines and a veritable
host of radio transceivers.  The main building is not build in a
bunker but built not far from the runways.  This has left the whole
facility extremely vunrable to a first strike nuclear or stealth
attack but all attempts to move it underground have lead to the whole
system failing apart.  Instead a backup was built but given the
endemic problem of getting parts, it is possible the backup has been
looted and canibalised beyond working order.

\section{The B-4 program}

At the start of the 1990s it became clear that the B-2 stealth bomber
project was not going to meet expectations and the then President
Clinton instigated the B-3 project to replace the aging B-52 fleet.
Instead of opting for a new plane the program recommended cutting back
on the B-2 and instead extending the life of the B-52 until 2040.  This
came as a shock to the industrial-military complex, who pushed for a
completely new plane.

With the arrival of George W Bush as president they got their way and
the secret B-4 project was born.  Given the trouble with the B-2 and
A-12 projects it was recommended that the existing B-2 frame be used.
The avionics were taken from the JSF program while the plane's skin
was taken from the NASA spaceplane project.  While this made the plane
inherently less stealthy than the B-2 is was much more robust.  The
rapid improvement in computing power and especially complex signal
processing, taken from the mobile communications industry, especially
the W-CDMA base station processors, gave the plane the ability to
actively cancel radar signals.

In addition the plane used the latest pulse-jet engines, enabling it
to fly at supercruise for up to 8,000 miles.  By utilising the
existing body frames of the B-2 the program was able to to produce its
first test plane by 2002 and extensive testing began in 2003, mainly
to test low level flight against the Soviet early warning systems.
Security on the program is extremely tight so any espionage is likely
to come from a long term sleeper.  All flight must have three crew
to avoid hijacking.

\end{multicols}

\end{document}
